Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-08 paper/paper.tex
Convert graphs to PDF

\begin{figure}
    \centering
    \includegraphics[scale=0.47]{figures/simple_topo_overall.png}
    \caption{Query completion time}\label{fig:micro_benchmark_total_time}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.47]{figures/simple_topo_closer_8.png}
    \caption{Sub query completion time}\label{fig:sub_query_completion_8}
\end{figure}

@@

\begin{figure}
    \includegraphics[scale=0.47]{figures/simple_topo_varying_bd.png}
    \caption{Query completion time with varying link capacity}\label{fig:varying_bd}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale=0.47]{figures/simple_topo_overall.pdf}
    \caption{Query completion time}\label{fig:micro_benchmark_total_time}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.47]{figures/simple_topo_closer_8.pdf}
    \caption{Sub query completion time}\label{fig:sub_query_completion_8}
\end{figure}

@@

\begin{figure}
    \includegraphics[scale=0.47]{figures/simple_topo_varying_bd.pdf}
    \caption{Query completion time with varying link capacity}\label{fig:varying_bd}
\end{figure}
